\chapter*{Acknowledgements}
%\addcontentsline{toc}{chapter}{Acknowledgements}

There have been several people instrumental in the development of me as an individual, and inspirational in the journey of my work, and I shall perpetually endeavour to repay their kindness. For now, allow me to express my sincerest thanks. 

I'd like to express my undying gratitude to my parents, Sarbari and Badal De. Without their constant support, teaching and guidance, I wouldn't have had the internal compass to choose right from wrong, or the drive and determination to strive for milestones. For me, they have embodied hard work and honesty, and taught by example; for which, I'm eternally grateful. I extend thanks to Akansha De, adjusting to a tabletop that lay strewn with my books and a shared computer that was always running some script or program for me. 

Words fail to convey the magnitude of inspiration, growth and learning that I have received on account of my supervisor Prof. Avik Bhattacharya. He has been a constant influence on me over the past half a decade or so, and a source of strength, courage, determination, and guidance; both through words and actions. For which I am deeply thankful. I would also like to thank my research proposal council members Prof. Alok Porwal and Prof. Subhasis Chaudhuri whose inputs have been invaluable to my work.

I'm also perpetually indebted to other professors that have been instrumental in directing my work, both here at IIT Bombay, and during my brief spells as a visiting researcher at the University of Trento and FBK. I'd like to begin with Prof. Subhasis Chaudhuri, who has actively participated in guiding my work, leading to massive improvements in its quality. During my spells in Italy, Prof. Lorenzo Bruzzone made sure to take time from his busy schedule to always answer my queries and check my work. I feel compelled to especially thank Dr. Francesca Bovolo for tirelessly smoothing the language, structure, and flow of my papers, and for her constant support and advice, academic and otherwise, during my stay at her lab, and beyond. An incident I want to highlight here is during my visiting period, Treno experienced a colder than usual bout of weather, and the jacket I had brought with me was insufficient. Without me having to ask, Francesca lent me a spare one. It is this kindness and hospitality I can never repay. 

My academic journey has been shaped by every teacher that has taught me, but specifically, I must thank Kavitha Alvares Mendonsa for having belief in my abilities even when I began to question them and Prof. Anuja Keni for sparking my interest in signal and image processing, Prof. Y. S. Rao and Dr. Anup Das for helping shape my interests into a passion and  Prof. Biplab Banerjee for his gentle but firm direction which has largely help shape this journey of exploration I am currently on. Several teachers have guided my thoughts from across the seas and far beyond. I'd like to thank Prof. Alejandro C. Frery and Prof. B. S. Daya Sagar, for their steady assistance with statistics and information theory, guidance and reassurances, Prof. Rosen for being personally inspiring and professionally guiding, Prof. Yoshio Yamaguchi and Prof. Ridha Touzi for our conversations about polarimetry, Prof. Devis Tuia and Prof. Akira Hirose for the exchanges we have had on the state of machine learning, neural networks, and computer vision. 

I want to thank my labmates both here, and in Trento for their company, discussion, and encouragement. At IIT, Dr. Surendar Manikam for continuing to be a personal mentor to me, Debanshu Ratha for his perspective, Arnab Muhuri for the adventures we have had (including the time we nearly died), Prof. Varsha Turkar for getting me started with classification studies, Prof. Sanjay Shitole for the directions we explored together academically and otherwise, Siddharth Hariharan, Swinky Dhingra and Dikshya Ratha for the conversations. In Trento, I can't thank enough Dr. Massimo Zanetti for reigniting my interest in mathematics, personal friendship and for the book that shall always remain on my bookshelf, Davide Pirrone for all the discussions both in person and over Skype which I'm sure we will continue to have, Claudia Paris for her advice, Ana-Maria Ilisei for the conversations and Davide Castelletti for his constant support. On reflection, I have made fast friends of my coworkers, and that in my view is my greatest achievement and source of pride. 

Last but definitely not the least, I'd like to thank Komal Desai for her encouragement, support, occasional admonishment and for being ever willing to review and proofread any body of work I send her, even at odd hours of the night. But over and beyond that, for instilling in me a belief in myself. It would be remiss not to acknowledge the contributions of Karishma Grover, Kannagi Desai, Nikhil Chinnari, Purav Motiwalla, and Vritti Goel for their steadfast friendship over the years. They have been my pillars and foundations, for which I am deeply thankful. 

With my sincerest apologies, I must recognize that there have several others who have profoundly contributed to my development and sense of self, that has ultimately guided my work, and invariably this thesis, but at this moment, my memory constraints me in expressing my gratitude. 

\vspace{2em}
\begin{flushleft}
\hspace{4.3in}Sincerely,\\
\hspace{4.3in}Shaunak De
\end{flushleft}