
\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}

\section*{Publications in Peer-Reviewed Journals}
{\small
\begin{enumerate} 

\item \ding{97}\quad \textbf{Shaunak De}, Debanshu Ratha, Dikshya Ratha, Avik Bhattacharya, and Subhasis Chaudhuri (2018). Tensorization of Multi-Frequency PolSAR Data for Classification Using an Auto-Encoder Network. IEEE Geoscience and Remote Sensing Letters. vol. 15, no. 4, 2018.

\item \ding{97}\quad \textbf{Shaunak De}, Lorenzo Bruzzone, Avik Bhattacharya, Francesca Bovolo and Subhasis Chaudhuri (2017). A Novel Technique Based on Deep Learning and a Synthetic Target Database for Classification of Urban Areas in PolSAR Data. IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing, vol. 11, no. 1, pp. 157-170, 2017. 

\item \ding{97}\quad Debanshu Ratha, \textbf{Shaunak De}, Turgay Celik and Avik Bhattacharya (2017). Change Detection in Polarimetric SAR Images Using a Geodesic Distance Between Scattering Mechanisms. IEEE Geoscience and Remote Sensing Letters. vol. 14, no. 7, pp. 1066-1070, 2017. 

\item Sanjay Shitole, Mayank Sharma, \textbf{Shaunak De}, Avik Bhattacharya, Y. S. Rao and B. K. Mohan (2017). Local contrast based adaptive SAR speckle filter. Journal of the Indian Society of Remote Sensing, 45(3), 451-462.

\item Avik Bhattacharya, Alok Porwal, Swinky Dhingra, \textbf{Shaunak De}, G. Venkataraman (2015). Remote estimation of dielectric permittivity of lunar surface regolith using compact polarimetric synthetic aperture radar data. Advances in Space Research, 56(11), 2439-2448.

\item Sanjay Shitole, \textbf{Shaunak De}, Y.S. Rao, B.K. Mohan and Anup Das (2015). Selection of suitable window size for speckle reduction and deblurring using SOFM in polarimetric SAR images. Journal of the Indian Society of Remote Sensing, 43(4), 739-750.

\item Avik Bhattacharya, Arnab Muhuri, \textbf{Shaunak De}, Surendar Manickam and A.C. Frery (2015). Modifying the Yamaguchi four-component decomposition scattering powers using a stochastic distance. IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing, vol. 8, no. 7, pp. 3497-3506, 2015.

\item Sanjay Shitole, \textbf{Shaunak De}, Y.S. Rao, B.K. Mohan and Anup Das (2015). MMSE based seed selection in IDAN speckle filter with point target preservation. International Journal of Imaging and Robotics, 15(3), 14-34.

\item Avik Bhattacharya, \textbf{Shaunak De}, Arnab Muhuri, Surendar Manickam, G. Venkataraman and Anup Das (2015). A new compact polarimetric SAR decomposition technique. Remote Sensing Letters, 6(12), 914-923.

\end{enumerate}
}
\section*{Publications in International Conference Proceedings}
{\small
\begin{enumerate} 

\item \ding{97}\quad \textbf{Shaunak De}, Davide Pirrone, Francesca Bovolo, Lorenzo Bruzzone and Avik Bhattacharya (2017, July). A novel change detection framework based on deep learning for the analysis of multi-temporal polarimetric SAR images. In Geoscience and Remote Sensing Symposium (IGARSS), 2017 IEEE International, pp. 4554-4557.

\item \ding{97}\quad Davide Pirrone, \textbf{Shaunak De}, Francesca Bovolo, Lorenzo Bruzzone and Avik Bhattacharya (2017, July). Unsupervised change detection in built-up areas by multi-temporal polarimetric SAR images. In Geoscience and Remote Sensing Symposium (IGARSS), 2017 IEEE International, pp. 5193-5196. 

\item \textbf{Shaunak De}, Abhishek Maity, Vritti Goel, Sanjay Shitole, and Avik Bhattacharya. "Predicting the popularity of instagram posts for a lifestyle magazine using deep learning." In Communication Systems, Computing and IT Applications (CSCITA), 2017 2nd International Conference on, pp. 174-177. IEEE, 2017.

\item \ding{97}\quad Biplab Banerjee, \textbf{Shaunak De}, Surendar Manickam, and Avik Bhattacharya. "An unsupervised hidden Markov random field based segmentation of polarimetric SAR images." In Geoscience and Remote Sensing Symposium (IGARSS), 2016 IEEE International, pp. 1536-1539. IEEE, 2016. 

\item Gaurav Kumar Dashondhi, Jyotirmoy Mohanty, Laxmi Narayana Eeti, Avik Bhattacharya, \textbf{Shaunak De}, and Krishna Mohan Buddhiraju. "A learning tool for optical and microwave satellite image processing and analysis." In Multispectral, Hyperspectral, and Ultraspectral Remote Sensing Technology, Techniques and Applications VI, vol. 9880, p. 988024. International Society for Optics and Photonics, 2016.

\item \ding{97}\quad \textbf{Shaunak De} and Avik Bhattacharya. "Urban classification using PolSAR data and deep learning." In Geoscience and Remote Sensing Symposium (IGARSS), 2015 IEEE International, pp. 353-356.  

\item Avik Bhattacharya, Arnab Muhuri, \textbf{Shaunak De}, M. Surendar, and G. Venkataraman. "A New Target Decomposition Technique for Compact Polarimetric SAR Data." In Lunar and Planetary Science Conference, vol. 46, p. 1065. 2015.

\item Avik Bhattacharya, M. Surendar, \textbf{Shaunak De}, Gopalan Venkataraman, and Gulab Singh. "Snow wetness estimation from dual polarimetric coherent TerraSAR-X data." In Geoscience and Remote Sensing Symposium (IGARSS), 2014 IEEE International, pp. 2766-2769.

\item Avik Bhattacharya, Arnab Muhuri, \textbf{Shaunak De}, and Alejandro C. Frery. "Orientation angle estimation from PolSAR data using a stochastic distance." In Geoscience and Remote Sensing Symposium (IGARSS), 2014 IEEE International, pp. 3474-3477. 

\item Siddharth Hariharan, Siddhesh Tirodkar, \textbf{Shaunak De}, and Avik Bhattacharya. "Variable importance and random forest classification using RADARSAT-2 PolSAR data." In Geoscience and Remote Sensing Symposium (IGARSS), 2014 IEEE International, pp. 1210-1213. 

\item \textbf{Shaunak De}, Vineet Kumar, and Y. S. Rao. "Crop Classification using RISAT-1 Hybrid Polarimetric SAR Data." In EUSAR 2014; 10th European Conference on Synthetic Aperture Radar; Proceedings of, pp. 1-4. VDE, 2014.

\item \textbf{Shaunak De}, Rao, Y. S., Vineet Kumar, and Anup Das. "Full and Hybrid Polarimetric SAR Data Analysis for Various Land." International Experts Meet on Microwave Remote Sensing,, Ahmedabad, India Features (2013): 16-17.

\item Varsha Turkar, \textbf{Shaunak De}, G. G. Ponnurangam, Rinki Deo, Y. S. Rao, and Anup Das. "Classification of RISAT-1 hybrid polarimetric data for various land features." In Synthetic Aperture Radar (APSAR), 2013 Asia-Pacific Conference on, pp. 494-497. 

\item Varsha Turkar, \textbf{Shaunak De}, Y. S. Rao, Sanjay Shitole, Avik Bhattacharya, and Anup Das. "Comparative analysis of classification accuracy for RISAT-1 compact polarimetric data for various land-covers." In Geoscience and Remote Sensing Symposium (IGARSS), 2013 IEEE International, pp. 3586-3589. 

\item \textbf{Shaunak De}, Rinky Deo, G. Raghuram, \& Y.S. Rao, “Software Development for Polarimetric SAR Data Processing: PolSDP.” In International Conference on Microwave Antenna, Propagation \& Remote Sensing, 2012.


\end{enumerate}
}
\vspace{1cm}
\begin{center}
\ding{97}\quad These publications have evolved from the doctoral dissertation.
\end{center}










